Charity analysis

### 2022-07-18 Shiny/Test/Flexdashboard rows.Rmd
Icon tests, tabs.

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
       flexdashboard, MetBrewer)
```

Column {.sidebar}
-----------------------------------------------------------------------

@@

@@

@@

@@

    # Creating data frame from Excel file
    exceldata <- reactive({
      widen_excel(input$excel$datapath)
    })
#---- Value Box ----------------------------------------------------------------    
    # Creating value box
    KPI_admin <- reactive({exceldata() |> 
           mutate(
    KPI_admin =
      str_c(
        format(
        (expenses_administrative / expenses_program_services *100), digits = 3
        ), "%"
        )
  ) |> 
  filter(year == max(year)) |> 
  select(KPI_admin) |> 
  str_flatten()
    })

    output$KPI_box <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "admin",
        color = "info",
        icon = "fa-random"
      )
    })

  output$KPI_box2 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "admin",
        color = "info",
        icon = "fa-random"
      )
    })
    output$KPI_box3 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "admin",
        color = "info",
        icon = "fa-random"
      )
    })

    output$KPI_box4 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "admin",
        color = "info",
        icon = "fa-random"
      )
    })

@@

    output$fancyplot <- renderPlotly(
      fancyplot()
    )
  })
```

@@

# Function to read Excel file
widen_excel <- function(file){
    read_excel(file) |> 
      mutate(
        Value = Value * 1000
      ) |> 
      unite(
        entry, c(Category, Name), sep = "_"
      ) |> 
      select(-`Sub-category`) |> 
      pivot_wider(names_from = entry, values_from = Value) |> 
      clean_names()
}

>>>>

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
       flexdashboard, MetBrewer, DT, fontawesome)
htmltools::tagList(fontawesome::fa_html_dependency())
```

Sidebar {.sidebar}
=======================================================================

@@

Dashboard
=======================================================================

@@

### KPI 5
```{r}
valueBoxOutput("KPI_box5")
```

@@

Details
=======================================================================

### Information 1

The KPIs are based on the following calculations

- **admin** is based on dividing
```{r}

### Information 2
```{r}

@@

    # Creating data frame from Excel file
    exceldata <- reactive({
      widen_excel(input$excel$datapath)
    })

#---- Value Boxes ----------------------------------------------------------------

    # Creating value box
    KPI_admin <- reactive({exceldata() |> 
           mutate(
    KPI_admin =
      str_c(
        format(
        (expenses_administrative / expenses_program_services *100), digits = 3
        ), "%"
        )
  ) |> 
  filter(year == max(year)) |> 
  select(KPI_admin) |> 
  str_flatten()
    })

    output$KPI_box <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "admin",
        color = "primary",
        icon = "fa-random"
      )
    })

    # Duplicate value boxes for testing
  output$KPI_box2 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "danger",
        color = "danger",
        icon = "fa-random"
      )
    })
    output$KPI_box3 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "success",
        color = "success",
        icon = "fa-random"
      )
    })

    output$KPI_box4 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "info",
        color = "info",
        icon = "fa-random"
      )})

      output$KPI_box5 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "admin",
        color = "warning",
        icon = "fal fa-abacus"
)})

@@

    output$fancyplot <- renderPlotly(
      fancyplot()
    )
})

@@

# Function to read Excel file
widen_excel <- function(file){
    read_excel(file) |> 
      mutate(
        Value = Value * 1000
      ) |> 
      unite(
        entry, c(Category, Name), sep = "_"
      ) |> 
      select(-`Sub-category`) |> 
      pivot_wider(names_from = entry, values_from = Value) |> 
      clean_names()
}
```
